Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-09 paper.tex
trying to get more data; minor changes in paper

\begin{document}
\title{Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications}
\author{Wesley Chen, Brandon Sim, Andy Shi \\
Harvard University, Applied Math 205 Final Project}
\date{December 15, 2014}

@@

\subsection{Comparison to Serial with $g_{fine}$ as \\a Forward Euler with
Smaller $\Delta t$}

\subsection{Comparison to Serial with $g_{fine}$ as \\Higher Order Methods}

\subsection{Comparison to a Forward Euler \\Parallelized by Space}

>>>>

\begin{document}
\title{Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications}
\author{Wesley Chen, Brandon Sim, Andy Shi \\
Harvard University, Applied Math 205 Final Project}
\date{December 10, 2014}

@@

\subsection{Comparison to Serial with $g_{fine}$ as a Forward Euler with
Smaller $\Delta t$}

\subsection{Comparison to Serial with $g_{fine}$ as Higher Order Methods}

\subsection{Comparison to a Forward Euler Parallelized by Space}
